### 2022-05-17 readme.Rmd
update many changes to pass R checks. Need to do this before I tweak with c++ headers.

## ppmData is an R package that can be used to set up a quadrature scheme for multiple species point processes modelling and could be used in [ecomix](https://github.com/skiptoniam/ecomix) or for other multiple species Point Processes.

>>>>

## ppmData is an R package that can be used to set up a quadrature scheme for spatial point processes modelling and could be used in [ecomix](https://github.com/skiptoniam/ecomix) to run multiple species Point Processes.
